Network Data Collection for Artifical Intelligence

### 2020-02-24 paper2/paper2.tex
Added some more content

Another aspect which has been examined is the stability of features in terms of time (year 2000/2001 vs. 2008) and location (Internet core vs. Internet edge). In this regard, the packet size can be considered a stable feature \cite{este2009}.

@@

@@

Timeslot features are extracted by counting the number of certain events in fixed time intervals. For the detection of DoS and probing traffic, the following timeslot features are proposed in \cite{waizumi2007}:
\begin{itemize}
	\item Number of TCP, UDP and ICMP packets
	\item Number of bytes sent and received through all TCP connections
	\item Number of TCP ports
	\item Number of occurences of TCP flags
	\item Number of DNS packets
	\item Number of fragmented packets
	\item Number of values of the four fields of IP addresses
\end{itemize}

@@

A different approach is to define features which measure specific behavioral differences between benign and malicious software. The UNSW-NB15 datasets contains mostly flow statistical features, but also a few features based on behavior \cite{Nb2015}:
\begin{itemize}
	\item A binary value denoting if the source and destination IP addresses and port numbers are equal
	\item Service (HTTP, FTP, SMTP, SSH, DNS, or IRC)
	\item Pipelined depth into the connection of HTTP request/response transaction
	\item Actual uncompressed content size of the data transferred from the server's HTTP service
	\item Number of flows containing HTTP GET and POST methods
	\item A binary value denoting if a FTP session is accessed by user and password
	\item Number of flows containing FTP commands
\end{itemize}

@@

In addition to the feature vectors, datasets to be used for supervised learning need to include labels. For the purpose of intrusion detection, each record (e.g., network flow) has to be labelled  binary as benign or malicious traffic, or nominally to distinguish between certain attack types. For example, the UNSW-NB15 dataset defines a binary label (0 for normal and 1 for attack) and a nominal label ("Normal" for benign traffic and "Fuzzers", "Analysis", "Backdoors", "DoS", "Exploits", "Generic", "Reconnaissance", "Shellcode" or "Worms" for the various attack types) \cite{Nb2015}. For some applications, there may also be a nominal label for benign traffic (e.g., browsing, chat, mail, P2P, streaming, VoIP) \cite{bagui2017}.

For data generated by simulated attacks, the labels can simply be based on the schedule of simulated attacks in combination with the IP addresses, ports and protocols involved \cite{Ids2018}.

@@

@@

@@

>>>>

Other methods which can be used for that purpose are based on association rule mining (ARM) \cite{moustafa2015}, sequential forward selection (SFS) \cite{dehghani2010, xu2015}, or the T-test \cite{sopuru2019},

When selecting the features, their limitations should be considered as well. Some features can easily be spoofed by attackers, while others are unable to detect encrypted malware traffic or cause performance problems. The development of new evasion techniques (e.g., disguising malicious traffic in widely used protocols such as HTTP) make the detection even harder \cite{celik2015}.

Another aspect which has been examined is the stability of features in terms of time (year 2000/2001 vs. 2008) and location (Internet core vs. Internet edge). In this regard, the packet size can be considered a stable feature \cite{este2009}. The suitability of features also depends on the type of network which is analyzed. For example, industrial control system networks are relatively static regarding IP address and port allocation, protocols and settings used, and number of connections, therefore features based on these attributes may provide good results in that particular environment \cite{mantere2013}.

@@

The open-source Java software CICFlowMeter can be used to extract features of network flows (which end either by TCP FIN packet, or a configurable timeout) from pcap files. It allows to select from a list of available features, but can also be extended to support new features \cite{cicflowmeter}, and has therefore been used in various applications \cite{Ids2018, lashkari2017, sopuru2019}.

\begin{figure}[htpb]
\centerline{\includegraphics[scale=0.35]{hast-ids.png}}
\caption{Feature learning process of HAST-IDS \cite{wang2018}}
\label{hast-ids}
\end{figure}

The hierarchical spatial-temporal feature-based intrusion detection system (HAST-IDS), which is shown in fig.~\ref{hast-ids}, also extracts flow-based features. However, it first transforms the bytes of network flows (HAST-I) or packets (HAST-II) into images using one-hot encoding (OHE), and then uses deep convolutional neural networks (CNNs) and long short-term memory (LSTM) networks to learn features based on these images \cite{wang2018}.

@@

Timeslot features are extracted by counting the number of certain events in fixed time intervals. For the detection of DoS and probing traffic, the following timeslot features are proposed \cite{waizumi2007}:
\begin{itemize}
	\item Number of TCP, UDP and ICMP packets
	\item Number of bytes sent and received through all TCP connections
	\item Number of TCP ports
	\item Number of occurences of TCP flags
	\item Number of DNS packets
	\item Number of fragmented packets
	\item Number of values of the four fields of IP addresses
\end{itemize}

@@

A different approach is to define features which measure specific behavioral differences between benign and malicious software.

One system following that approach is called "traffic aggregation for malware detection". It defines three characteristics which can be combined to distinguish between benign and malware traffic \cite{yen2011}:
\begin{itemize}
	\item Common destinations (assuming that compromised systems contact different hosts than uncompromised systems)
	\item Similar payload (assuming that command-and-control traffic uses common protocol syntax)
	\item Common software platforms (assuming that malware usually relies upon a specific operating system and also specific applications, such as web browsers)
\end{itemize}

The UNSW-NB15 datasets contains mostly flow statistical features, but also a few features based on behavior \cite{Nb2015}:
\begin{itemize}
	\item A binary value denoting if the source and destination IP addresses and port numbers are equal
	\item Service (HTTP, FTP, SMTP, SSH, DNS, or IRC)
	\item Pipelined depth into the connection of HTTP request/response transaction
	\item Actual uncompressed content size of the data transferred from the server's HTTP service
	\item Number of flows containing HTTP GET and POST methods
	\item A binary value denoting if a FTP session is accessed by user and password
	\item Number of flows containing FTP commands
\end{itemize}

@@

In addition to the feature vectors, datasets to be used for supervised learning need to include labels. For the purpose of intrusion detection, each record (e.g., network flow) has to be labelled  binary as benign or malicious traffic, or nominally to distinguish between certain attack types. For example, the UNSW-NB15 dataset defines a binary label (0 for normal and 1 for attack) and a nominal label ("Normal" for benign traffic and "Fuzzers", "Analysis", "Backdoors", "DoS", "Exploits", "Generic", "Reconnaissance", "Shellcode" or "Worms" for the various attack types) \cite{Nb2015}. For some applications, there may also be a nominal label for benign traffic (e.g., browsing, chat, mail, P2P, streaming, VoIP) \cite{lashkari2017, bagui2017}.

For data generated by simulating attacks, the labels can simply be based on the schedule of simulated attacks in combination with the IP addresses, ports and protocols involved \cite{Ids2018}.

@@

\bibitem{moustafa2015} Moustafa, N. and Slay, J. (2015). The significant features of the UNSW-NB15 and the KDD99 data sets for Network Intrusion Detection Systems. 2015 4th International Workshop on Building Analysis Datasets and Gathering Experience Returns for Security (BADGERS), Kyoto, pp. 25-31, 2015.
\bibitem{dehghani2010} Dehghani, F. and Movahhedinia, N. and Khayyambashi, M. R. and Kianian, S. (2010). Real-time Traffic Classification Based on Statistical and Payload Content Features. 2010 2nd International Workshop on Intelligent Systems and Applications, Wuhan, pp. 1-4, 2010.
\bibitem{sopuru2019} Sopuru, J. and Sari, A. and Akkaya, M. (2019). Modeling A Malware Detection And Categorization System Based On Seven Network Flow-Based Features. International Journal of Innovative Technology and Exploring Engineering (IJITEE), vol. 8(7), pp. 2982-2989, 05 2019

@@

\bibitem{mantere2013} Mantere, M. and Sailio, M. and Noponen, S. (2013). Network Traffic Features for Anomaly Detection in Specific Industrial Control System Network. Future Internet, vol. 5, pp. 460-473, 2013

@@

\bibitem{cicflowmeter} Canadian Institute for Cybersecurity (CIC) (2016). Applications | Research | Canadian Institute for Cybersecurity | UNB. [online] Available at: \url{https://www.unb.ca/cic/research/applications.html#CICFlowMeter} [Accessed 24 Feb. 2020].
\bibitem{lashkari2017} Lashkari, A. H. and Gil, G. D. and Mamun, M. S. I. and Ghorbani, A. A. (2017). Characterization of Tor Traffic using Time based Features. Proceedings of the 3rd International Conference on Information Systems Security and Privacy (ICISSP 2017), pp. 253-262, 2017.
\bibitem{wang2018} Wang, W. and Sheng, Y. and Wang, J. and and Zeng, X. and Ye, X. and Huang, Y. and Zhu, M. (2018). HAST-IDS: Learning Hierarchical Spatial-Temporal Features Using Deep Neural Networks to Improve Intrusion Detection. IEEE Access, vol. 6, pp. 1792-1806, 2018.
\bibitem{yen2011} Yen, T. (2011). Detecting stealthy malware using behavioralfeatures in network traffic. PhD thesis, Carnegie Mellon University, 2011.
